Sperm should evolve to make female meiosis fair.

### 2014-05-19 writeup_and_notes/signif_statement.tex
updated the signif statement

There are a number of evolutionary mystries concerning meiosis, however,little attention has been directed at the odd fact that fertilization by sperm is required to complete female meiosis in many species of animal. 
At first sight this seems strange as it seems to presents a dangerous opportunity for selfish alleles in sperm to distort the outcome of female meiosis in their own favor creating the opportunity for conflicts between male and female genomes. In this paper, through mathematical modeling, we show that in fact quite the opposite is true, sperm are usually selected to ensure the fairness of meiosis.
Intuitively this comes about because selfish sperm have to immediately suffer any ill consequences of their actions in the resulting zygote, and so it is strongly in sperm's interests to keep female meiosis fair.
We hypthosize that the wide-spread requirement of fertilization to complete female meiosis may represent a long-term 
collaboration between male and female gametes to ensure fairness and the production of high quality gametes.

>>>>

Evolutionary biologists are fascinated by the oppotunities for benefits, costs, and opportunities for conflict during meiosis, however,little attention has been directed at the odd fact that fertilization by sperm is required to complete female meiosis in many species of animal. At first sight this seems strange as it seems to presents a dangerous opportunity for selfish alleles in sperm to distort the outcome of female meiosis in their own favor creating the opportunity for conflicts between male and female genomes. In this paper, through mathematical modeling, we show that in fact quite the opposite is true, sperm are usually selected to ensure the fairness of meiosis. Intuitively this comes about because selfish sperm have to immediately suffer any ill consequences of their actions in the resulting zygote, and so it is strongly in sperm's interests to keep genomes from gaming female meiosis. We hypthosize that the wide-spread requirement of fertilization to complete female meiosis may represent a long-term collaboration between male and female gametes to ensure fairness and the production of high quality gametes.
